Inferring Invariants of Distributed Programs

### 2015-05-01 Doc/approach.tex
Make it wider

\begin{figure}
\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 0}, label=lst:node0]
    Integer a := 1
    Integer b := 2
    send ( a + '_' + b )
    recv (buf)
    Integer result := parse (buf)
\end{lstlisting}
\end{figure}

\begin{figure}
\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 1}, label=lst:node1]
    recv (buf)
    Integer first := getFirstOperand( buf )
    Integer second := getSecondOperand( buf )
    Integer sum := first + second
    send ( sum )
\end{lstlisting}
\end{figure}

As mentioned earlier, the naive approach for inferring these invariants will be to dump all
state variable values at all program points and feed them to an
invariant detector like Daikon\cite{ernst2007daikon}. But given the
number of program points and huge number of variables in a relatively
large program this approach is not scalable. Moreover, it can result in inferring incorrect invariants that are hold by accident. So we propose two main
optimizations to reduce the number of program point, variable value
combinations.

@@

\begin{figure}
\begin{subfigure}[b]{\linewidth}
\centering
 \begin{lstlisting}[]
	recv(n)
	i := 1
	sum := 0
	product := 1
	for i <= n {
		sum := sum + i
		product := product * i
		i := i + 1
	}
	send(sum)
	send(product)
\end{lstlisting}
        \vspace{-2mm}
                \caption{A Go Program}
        \end{subfigure}

\begin{subfigure}[b]{\linewidth}
\centering
\begin{lstlisting}[]
	recv(n)
	i := 1

@@

	send(product) // backward slice from here
\end{lstlisting}
        \vspace{-2mm}
                \caption{Go program backward sliced at line 10}
%                \label{Fig:refactored}
        \end{subfigure}
                        \caption{Backward slice of a Go program \cite{Tip} }
                \label{Fig:backslice}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth,scale=0.5]{images/pdg.png}
  \caption{Program Dependence Graph of Example Program in Figure \ref{Fig:backslice}}
  \label{fig:expdg}
\end{figure}

@@

Overall execution flow of the analysis is illustrated in Figure~\ref{fig:go_flow} and works as follows:
\begin{itemize}
\item Developer annotates interesting program points in the Go program which will be used as states for mining invariants.
\item Program Dependence Graph is computed and based on the location of send, receive and developer annotated points, set of variables that contribute to distributed state of the system and thus should be dumped at each point is determined
\item Program is instrumented to dump selected variable values, their type and current vector clock at the annotated program points at run time
\item Based on the vector clock of each log, logs are paired to each other and combined variable values of two logs is fed to the daikon in its specific format.
%For this we are hoping to use static analysis libraries
%available under Go-lang Parse package and tools\cite{static_golang} which provide
%support for Identifier resolution, Type information, Call graph
%navigation and Channel peers (send $\leftrightarrow$ receive)
%identification.
%\item Then as the first step in the analysis phase, this instrumented program is executed using the test suites and program traces are collected.
%\item Forward flow analysis is done on the collected traces
%\item Using the results of the previous step, variables contributing to distributed state is identified.
%\item From the dumped variable values at annotated program points (after multiple executions), only the values of variables chosen in the previous step are selected.
%\item Selected variable values belonging to 2 distinct annotated program points in the 2 nodes are fed to Daikon for inferring invariants.
\end{itemize}

\begin{figure}
  \includegraphics[width=\columnwidth]{go_flow.pdf}
  \caption{Flow of the invariant inference of Go programs}
  \label{fig:go_flow}
\end{figure}

>>>>

\begin{figure}
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 0}, label=lst:node0]
    Integer a := 1
    Integer b := 2
    send ( a + '_' + b )
    recv (buf)
    Integer result := parse (buf)
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 1}, label=lst:node1]
    recv (buf)
    Integer first := getFirstOperand( buf )
    Integer second := getSecondOperand( buf )
    Integer sum := first + second
    send ( sum )
\end{lstlisting}
\end{minipage}\hfill
\end{figure}

%As mentioned earlier, the naive approach for inferring these invariants will be to dump all
%state variable values at all program points and feed them to an
%invariant detector like Daikon\cite{ernst2007daikon}. But given the
%number of program points and huge number of variables in a relatively
%large program this approach is not scalable. Moreover, it can result in inferring incorrect invariants that are hold by accident. So we propose two main
%optimizations to reduce the number of program point, variable value
%combinations.

Overall execution flow of the analysis is illustrated in Figure~\ref{fig:go_flow} and works as follows:
\begin{itemize}
\item Developer annotates interesting program points in the Go program which will be used as states for mining invariants.
\item Program Dependence Graph is computed and based on the location of send, receive and developer annotated points, set of variables that contribute to distributed state of the system and thus should be collected at each point is determined
\item Program is instrumented to log selected variable values, their type and current vector clock at the annotated program points at run time
\item Program is executed by test cases or appropriate inputs and logs of variables are collected
\item Based on the vector clock of each log, logs are paired to each other
\item Combined variable values of two logs is fed to the daikon in its specific format.
%For this we are hoping to use static analysis libraries
%available under Go-lang Parse package and tools\cite{static_golang} which provide
%support for Identifier resolution, Type information, Call graph
%navigation and Channel peers (send $\leftrightarrow$ receive)
%identification.
%\item Then as the first step in the analysis phase, this instrumented program is executed using the test suites and program traces are collected.
%\item Forward flow analysis is done on the collected traces
%\item Using the results of the previous step, variables contributing to distributed state is identified.
%\item From the dumped variable values at annotated program points (after multiple executions), only the values of variables chosen in the previous step are selected.
%\item Selected variable values belonging to 2 distinct annotated program points in the 2 nodes are fed to Daikon for inferring invariants.
\end{itemize}
In each of the following sections we explain each step in detail.
\begin{figure}
  \includegraphics[width=\columnwidth]{go_flow.png}
  \caption{Flow of the invariant inference of Go programs}
  \label{fig:go_flow}
\end{figure}

@@

\begin{figure}
\begin{minipage}{.45\textwidth}
\begin{subfigure}[b]{\linewidth}
\centering
 \begin{lstlisting}[]
	recv(n)
	i := 1
	sum := 0
	product := 1
	for i <= n {
		sum := sum + i
		product := product * i
		i := i + 1
	}
	send(sum)
	send(product)
\end{lstlisting}
        \vspace{-2mm}
                \caption{A Go Program}
        \end{subfigure}
\end{minipage}\hfill
\begin{minipage}{.45\textwidth}
\begin{subfigure}[b]{\linewidth}
\centering
\begin{lstlisting}[]
	recv(n)
	i := 1

@@

	send(product) // backward slice from here
\end{lstlisting}
        \vspace{-2mm}
                \caption{Go program backward sliced at line 10}
%                \label{Fig:refactored}
        \end{subfigure}
        \end{minipage}\hfill
                        \caption{Backward slice of a Go program \cite{Tip} }
                \label{Fig:backslice}
\end{figure}

%\begin{figure}
%\begin{subfigure}[b]{\linewidth}
%\centering
% \begin{lstlisting}[]
%	recv(n)
%	i := 1
%	sum := 0
%	product := 1
%	for i <= n {
%		sum := sum + i
%		product := product * i
%		i := i + 1
%	}
%	send(sum)
%	send(product)
%\end{lstlisting}
%        \vspace{-2mm}
%                \caption{A Go Program}
%        \end{subfigure}
%
%\begin{subfigure}[b]{\linewidth}
%\centering
%\begin{lstlisting}[]
%	recv(n)
%	i := 1
%
%	product := 1
%	for i <= n {
%		
%		product := product * i
%		i := i + 1
%	}
%	
%	send(product) // backward slice from here
%\end{lstlisting}
%        \vspace{-2mm}
%                \caption{Go program backward sliced at line 10}
%%                \label{Fig:refactored}
%        \end{subfigure}
%                        \caption{Backward slice of a Go program \cite{Tip} }
%                \label{Fig:backslice}
%\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth,scale=0.5]{images/pdg.png}
  \caption{Program Dependence Graph of Example Program in Figure \ref{Fig:backslice} \cite{Tip}}
  \label{fig:expdg}
\end{figure}

\subsection{Matching Logs with Vector Clocks}

@@
